---
title: "BIOS 6611 Materials"
output: 
  html_document:
    toc: true
    toc_float: true
---

<script>
$(document).ready(function(){
    $('[data-toggle="popover"]').popover(); 
});
</script>

```{r, echo=F, message=F}
library(kableExtra)
library(dplyr)
```

This page includes the asynchronous lecture videos, PDF slides, and other materials for Biostatistical Methods I (BIOS 6611). The material is broadly broken down by theme with links provided to download materials or view the videos.

*Page in progress.*

## Probability and Distributions

```{r, echo=F}
prob_dist_lectures <- c('Intro to Statistical Topics',
'Properties of Estimators',
'Simulations Studies',
'Brief, but Complete, Interpretations',
'Discrete Distributions',
'Common Discrete Distributions',
'Probability and Bayes Theorem',
'Methods of Estimation (MoM, MLE, LSE)',
'Continuous Distributions',
'The Normal Distribution',
'Assessing Normality in Samples',
'The Central Limit Theorem',
'Other Continuous Distributions',
'Deriving the Sampling Distribution of the Sample Mean and Sample Variance')

prob_dist_desc <- c('The starting point of BIOS 6611, where we discuss what is statistics/biostatistics, populations vs. samples, parameters vs. statistics, descriptive vs. inferential stats, and point vs. interval estimation.',
                    'An introduction to notation used for statistical estimation. Then bias, efficiency, mean square error, and asymptotic consistency are discussed as properties of estimators. An example using a simulation study in R is presented for the sample mean.',
                    'Simulation studies in R and the difference between the population distribution and sampling distribution.',
                    'Providing the point estimate, an interval estimate, our uncertainty (i.e., p-value), and our ultimate decision are the four elements to try and include in every brief, but complete, summary.',
                    'An introduction to discrete random variables and their probability mass function (PMF), cumulative density function (CDF), expected value, variance, and standard deviation.',
                    'The Bernoulli, Binomial, and Poisson distributions.',
                    'Joint, marginal, and conditional distributions/probabilities for bivariate distributions, with an introduction to Bayes\' theorem.',
                    'An introduction to Methods of Moments, Maximum Likelihood Estimation, and Least Squares Estimates.',
                    'Continuous random variables and their probability density function (PDF), cumulative density function (CDF), expected value, variance, and standard deviation.',
                    'The normal (Gaussian) distribution in all its glory!',
                    'Graphical and formal hypothesis tests to evaluate normality in a sample.',
                    'The central limit theorem (CLT) is one of the most consequential theorems in statistics. In this lecture we introduce the CLT and illustrate its power through a simulation study.',
                    'The chi-squared, F, and t distributions.',
                    'Deriving the sampling distributions of the sample mean and variance and their corresponding properties.'
)

prob_dist_pdf_link <- paste0('./files/bios6611/',
                             c('W1/StatisticalConcepts.pdf',
                               'W1/PropertiesOfEstimators.pdf',
                               'W1/Simulations.pdf',
                               'W1/BriefButCompleteInterpretations.pdf',
                               'W2/DiscreteData_PMF_EX_Var.pdf',
                               'W2/DiscreteDistributions.pdf',
                               'W2/Probability_Joint_Marginal_Conditional.pdf',
                               'W2/EstimatorMethods.pdf',
                               'W3/ContinuousData_PDF_EX_Var.pdf',
                               'W3/The_Normal_Distribution.pdf',
                               'W3/Assessing_Normality_in_Samples.pdf',
                               'W3/CentralLimitThm.pdf',
                               'W3/OtherContDistr_t_F_chisq.pdf',
                               'W3/Samping_Dist_Xbar.pdf'))
prob_dist_pdf <- paste0('[PDF](',prob_dist_pdf_link,')')

prob_dist_videos_link <-c('https://youtu.be/5tRJs1jAaRE',
  'https://youtu.be/AERMb-fkMWY',
  'https://youtu.be/u9Zq6ZdMthw',
  'https://youtu.be/pv-mCRuxVp8',
  'https://youtu.be/Uuy_r3itw5k',
  'https://youtu.be/84Nkyd8A0Qw',
  'https://youtu.be/rcGAXNdy9VQ',
  'https://youtu.be/idKDhP8Wo-w',
  'https://youtu.be/NBGvCw7yWUo',
  'https://youtu.be/fTe8NOjoY1E',
  'https://youtu.be/hW0cHyh7Xpo',
  'https://youtu.be/ppEgbv_ddXA',
  'https://youtu.be/lWeB25hRFuU',
  'https://youtu.be/Z2-6UenBYRI'
  )
prob_dist_videos <- paste0('[YouTube](',prob_dist_videos_link,')')

prob_dist <- data.frame(
  'Lecture' = prob_dist_lectures,
  'File' = prob_dist_pdf,
  'Video' = prob_dist_videos)

prob_dist$Lecture <- cell_spec(prob_dist$Lecture, popover = spec_popover(
  content = prob_dist_desc,
  title = 'General Overview',
  position = 'top'
))

kbl(x = prob_dist, escape=F, align='lcc', col.names = c('Lecture Topic','Slides','YouTube Link')) %>%
  column_spec(1, width='18em') %>%
  column_spec(2, width='5em') %>%
  column_spec(3, width='5em') %>%
  kable_styling(bootstrap_options = c("striped")) 
```


## Hypothesis Testing, Power, Sample Size


## Conditional Probability, Effect Measures, Inference for 2x2 Tables


## Bootstrap Sampling and Nonparametric Methods


## Simple Linear Regression


## Multiple Linear Regression